Solving Combinatorial Puzzles with Parallel Evolutionary Algorithms \thanks{This work was supported by a private funding of Velbazhd Software LLC.}

### 2019-02-13 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/paper.tex
Initila version of the full text paper.

@@

The experiments clearly show that the addition of Hausdorff distance component improves the performance of the genetic algorithm. Calculation of the Hausdorff distance is a little bit slower than the calculation of the Euclidean distance, but better solution fitness estimation generally leads to genetic algorithm convergence improvement. Investigation in the field of the soft computing can be done for the proposed fitness value evaluation as it was done in \cite{angelova01}.

>>>>

\begin{figure}
\includegraphics[width=0.75\textwidth]{fig03.png}
\centering
\caption{Algorihtm convergence with star topology.} \label{fig03}
\end{figure}
\FloatBarrier

Experiments are done in two groups with 30 independent runs for each. The source code originally is divided for test with star topology and incident nodes participation as migration strategies. That is why there are two groups of experiments. Each experiment compares pure Euclidean distance implementation and the proposed Hausdorff distance modification.

\begin{figure}
\includegraphics[width=0.75\textwidth]{fig04.png}
\centering
\caption{Algorihtm convergence with incident nodes participation.} \label{fig04}
\end{figure}
\FloatBarrier

Fig.\ref{fig03} shows that when star topology is used the advantage of Hausdorff modification is not so big, but as it is shown in Fig.\ref{fig04} when incident nodes participation is used the proposed modification leads to convergence seep-up.

@@

The experiments show that the addition of Hausdorff distance component improves the performance of the genetic algorithm. Calculation of the Hausdorff distance is a little bit slower than the calculation of the Euclidean distance, but better solution fitness estimation generally leads to genetic algorithm convergence improvement. Investigation in the field of the soft computing can be done for the proposed fitness value evaluation as it was done in \cite{angelova01}.
